\Large \bf Uncovering Distributed System Bugs during Testing (not Production!)

### 2015-08-29 methodology.tex
more text about modeling

\subsubsection{Test harness as \psharp state machines}
\label{sec:method:model:harness}

Draft

>>>>

\subsubsection{Creating a test harness using \psharp}
\label{sec:method:model:harness}

Before being able to use \psharp to test an existing distributed system, the environment of the components that the developer wants to test have to be modeled using the \psharp state machine APIs.  This involves creating mock classes that inherit from the \texttt{Machine} abstract class. The \texttt{Machine} class exposes methods for declaring a state machine (e.g. machine states and state transitions) as well as methods for sending events to other machines, declaring event handlers for received events, and accessing the payload from the latest received event.

In the Azure Storage vNext case study, we created the following \psharp machines: \texttt{Environment}, \texttt{ExtentNode}, \texttt{ExtentManager}, and \texttt{Timer}.

The \texttt{Environment} is essentially a ``god'' machine: it is the very first machine that is created; has a handle to all other machines in the harness; and includes the logic based on which the test harness will execute (e.g. how many nodes should be created, how many failures should occur, etc).

The \texttt{ExtentNode} machine is a model (less than 150 lines of code) of the real Extent Node and is responsible for generating synchronization events and sending them to the \texttt{ExtentManager} to test the extent manager's repair logic.

The \texttt{ExtentManager} is a wrapper machine and is used to connect the \psharp modeled code with the legacy \csharp code. A typical wrapper machine contains a handle (as a field) to the system component that is being wrapped (in our case the real Extent Manager object) and the event handlers are responsible for translating any received events to method calls in the real code that is being tested. The \texttt{ExtentManager} is accompanied by a mocked version of the real Network Engine class. The real Extent Manager is communicating with the outside world via remote procedure calls, but in \psharp harness we want to capture this communicating and expose it as calls to \psharp communicating primitives. This is discussed in detail in Section~\ref{sec:method:model:dispath}.

Finally, the \texttt{Timer} machine models the operating system timer and is responsible for triggering events related to the Azure Storage vNext logic (e.g. synchronization messages, heartbeats and repair logic loops). This is discussed in detail in Section~\ref{sec:method:model:timers}.
